\begin{remerciements}

I was once told that PhD is a long journey of transformation from a \emph{novice} to \emph{professional} researcher. To succeed, an individual can never do it alone; there must be someone who is there for this, providing all the helping hands and supports. I can’t agree more\revAnglais{,} and as for my case, I have a lot of people to thank.

First thanks must be to my supervisor, \emph{Prof. Adel M. Alimi}, who has been truly inspirational throughout my candidature. He always shows me a tireless enthusiasm to meet, discuss, listen and encourage. His invaluable \revAnglais{pieces of advice} and faith make all the difference, and I have been blessed to find in him all the good qualities of a supervisor.  

Many thanks must go to my co-supervisor, Dr. \emph{Anis Ben Ammar}, who has given all the extra guidance and help that prove to be precious in improving the quality of my work. 

I would like to hold this opportunity to express my gratitude and respect to the reviewers \textit{Prof. Sami Faiz} and \textit{Prof. Fakhreddine Karray}, to the exterminator \textit{Prof. Slim Kanoun} and to the chairman \textit{Prof. Chokri Ben Amar}, for their acceptance to evaluate this research work and their valuable remarks and feedback.


A special thanks to Dr. \textit{Nizar Elleuch} and Dr. \textit{Issam Feki} who were always concerned to provide me the necessary conditions for the completion of my thesis.

The \textsc{Regim-Lab} has provided me nice working places with all the much needed facilities, and services, as well as financial supports including travel allowances. Thanks to all the people there who have helped me with many things. 

I would like to acknowledge the financial support of this work by grants 
from General Direction of Scientific Research (DGRST), Tunisia, under the ARUB program.

I thank my wife \emph{Bochra} who is always there for me and makes this whole journey so enjoyable. 

Thanks to all my colleagues \emph{Kais} and \emph{Ghada} who have always given me tremendous supports and encouragement. 

Last, but most importantly, I’d like to dedicate this thesis for my father \emph{Salah} and my mother \emph{Monia} to express my deepest gratitude. They are the best parents who are so willing in giving me the best in life without hoping for anything in return. I am also so blessed to have \revAnglais{such} really loving sisters \emph{Mariem} and \emph{Rim} who gave me so much \revAnglais{support} and encouragement to do well during this candidature.

Above all, I thank my stepfather \emph{Mohamed Hechmi} and my stepmother \emph{Fatma} who have always given me tremendous supports and encouragement. I would like also to thank my stepbrothers  \emph{Kais}, \emph{Hamza}, \emph{Mohamed Hédi}, \emph{Mondher}, \emph{Mohamed Salah} and \emph{Abdelkarim} for supporting me spiritually throughout writing this thesis and \revAnglais{in} my life in general.
\\
\\
\\

Thanks to all\\
Mohamed ZARKA
\end{remerciements}
